### 2018-08-23 doc/latex/04-Code.tex
Add documentation for GenPop in manual

\subsection{Generating the geography}
\label{subsection:gengeo}
We start by generating the geographical component, we call this a GeoGrid.
This contains locations with an id, name, province, coordinates and nominative population figures.
These locations contain multiple ContactCenters, like Schools and Households, which in turn contain ContactPools.
This structure is internally generated by several ``Generators" and will afterwards be used by ``Populators" to fill the ContactPools.
We construct the following types of ContactCenter:

\begin{description}
    \item[K-12 Schools]:
        These schools contain on average 500 students, with an average of 20 students per class, which corresponds to 25 ContactPools.
        The total amount of schools in the region is determined by the size of the population and the fraction of those people who attend a K-12 school.
        These generated schools are then assigned to a location by a draw from a discrete distribution based on the relative population size in each location.
    \item[Colleges]:
        These contain an average of 3000 students and 150 students per ContactPool.
        They are exclusively assigned to the 10 biggest locations in terms of population size.
        Within those 10 locations we again use a discrete distribution based on the relative population of the city compared to the total population in these top 10 cities.
    \item[Workplaces]:
        The assignment of workplaces is analogous to that of K-12 schools, but now we account for commuting information to determine the actual number of workers in a location.
        We find this amount by the working people who live there plus the people that commute to this location minus the ones that live there but commute away.
        A workplace contains on average 20 people.
    \item[Communities]:
        We create both primary and secondary communities, each containing 2000 persons from all ages and occupations.
        The assignement is analogous to that of K-12 schools.
    \item[Households]:
        The number of households is determined by the average size of a household in the reference profile and the total population size.
        The assignement is again analogous to that of K-12 schools.
\end{description}

\subsection{Generating the population}
\label{subsection:genpop}
TODO

>>>>

\subsection{Generating the geography}
\label{subsection:gengeo}
We start by generating the geographical component, we call this a GeoGrid.
This contains locations with an id, name, province, coordinates and nominative population figures.
These locations contain multiple ContactCenters, like Schools and Households, which in turn contain ContactPools.
This structure is internally generated by several ``Generators" and will afterwards be used by ``Populators" to fill the ContactPools.
The different types of ContactCenters are created by a different partial generator for each type and added separately to the GeoGrid.
We construct the following types of ContactCenters:

\begin{description}
    \item[Households]:
        The number of households is determined by the average size of a household in the reference profile and the total population size.
        These generated households are then assigned to a location by a draw from a discrete distribution based on the relative population size in each location.
    \item[K-12 Schools]:
        These schools contain on average 500 students, with an average of 20 students per class, which corresponds to 25 ContactPools.
        The total amount of schools in the region is determined by the size of the population and the fraction of those people who attend a K-12 school.
        The assignment is analogous to that of households.
    \item[Colleges]:
        These contain an average of 3000 students and 150 students per ContactPool.
        They are exclusively assigned to the 10 biggest locations in terms of population size.
        Within those 10 locations we again use a discrete distribution based on the relative population of the city compared to the total population in these top 10 cities.
    \item[Workplaces]:
        The assignment of workplaces is analogous to that of households, but now we account for commuting information to determine the actual number of workers in a location.
        We find this amount by the working people who live there plus the people that commute to this location minus the ones that live there but commute away.
        A workplace contains on average 20 people.
    \item[Communities]:
        We create both primary and secondary communities, each containing 2000 persons from all ages and occupations.
        The assignment is again analogous to that of households.
\end{description}

\subsection{Generating the population}
\label{subsection:genpop}
After creating the structures that will allow people to come in contact with each other and spread possible infections, we have create the population itself and determine the different ContactPools they will be in.
The persons are created based on the Household profiles in the HouseholdPopulator.
Analogous to the creation of the ContactCenters, we have a partial populator that will populate its own type of ContactPool:

\begin{description}
    \item[Households]:
        To create the actual persons, we draw a random household from the list of sample households and use that as a template for the number of members and their ages.
        We simply do this for each household in the GeoGrid, since we already determined the locations and amount of households while generating the geography.
    \item[K-12 Schools]:
        We start by finding all schools within a 10km radius of the household location. If this list is empty, we double this searching radius until it's no longer empty.
        We then choose a random ContactPool from the combined list of ContactPools in the found schools, even if this ContactPool now has more students than average (20).
    \item[Colleges]:
        The students who study ``close to home" are assigned to a college in a way analogous to the assignment to K-12 schools.
        For the ones that study further from home we first determine the list of locations where people from this locations commute to and choose one of these locations by use of a discrete distribution based on the relative commuting information.
        After we have chosen a location, we randomly choose a ContactPool at a college this location and assign it to the commuting student.
    \item[Workplaces]:
        We first decide if the person actually has a job based on the unemployment parameter.
        We assign a workplace to an active worker that works ``close to home" in an analogous way as the assignment of K-12 schools to students.
        For the commuting workers we use a technique analogous to that of the commuting college students.
    \item[Communities]:
        The communities we can choose from at a location is determined in an analogous way to the K-12 schools.
        In primary communities we simply choose a random ContactPool from the list of Communities for each person in a household.
        In secondary communities however, we assign complete households to the ContactPools instead of each person in the household separately to a ContactPool.

\end{description}
